Update on simulation results and queries

### 2020-12-23 results_simulation.Rmd
minor change

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")

# How to design the alternate designs when distributions are actually different?

>>>>

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")
```
# How to design the alternate designs when distributions are actually different?
